### 2015-02-13 Article/Article.tex
13_02_2015

Table \ref{Parametres} represents a review of the state variables and the parameters used in the model. %We analyze the model step-by-step, starting from a simple case with herbivores competing for one plant and one resource, then several plants and one resource, then multiple resources embedded into one plant, and finally the complete model, with multiple resources embedded into multiple plants.
Indeed, resources are provided by several plants, and each plant provides several resources. %, which create a new level of complexity.
The first case is a spatial segregation of resources, while the second case is a stoichiometric balance issue between plant and herbivore.

\subsection*{Spatial segregation of resources}%Case 1: one plant species and one resource}
A given resources may be provided by only one plant or several plants, which creates a spatial segregation of resources. 
First of all, consider a simple model with $p$ herbivore species feeding on one plant species embedding a single %chemical element 
resource. 
In case of one resource involved, this resource ($R$) is assumed to be growth limiting.

@@

\begin{equation}
 \barre{H}_i=\frac{g_iQ_{vR}S-aQ_{hiR}m}{g_iQ_{hiR}m}
 \end{equation}
Therefore, at equilibrium, herbivore biomass increases with plant availability (supply) and resource quota in plant biomass ($Q_{vR}$), while it decreases with herbivore mortality and resource quota in herbivore biomass ($Q_{hiR}$). Resource availability at steady state is: 
\begin{equation}\label{oneresource}
\barre{R}_{hi}=\barre{V}Q_{vR}=\frac{S}{a+g_i\barre{H}_i}Q_{vR}
\end{equation}
This $\barre{R}_{hi}$ represents level of resource remaining available for another herbivore, it also represents the minimal threshold of resource availability for herbivore species $i$ (i.e., if resource availability is below this threshold this herbivore species cannot maintain a population at steady state). Indeed, it can be assimilated to Tilman's $R^*$.
Therefore, considering two herbivores (species 1 and species 2), if $g_1\barre{H}_1>g_2\barre{H}_2$, species 1 depletes resource below the threshold of species 2, and species 2 is excluded. %Therefore, competition between two herbivore limited by the same chemical resource embedded into one plant leads to competitive exclusion. 
In other words, the competitive exclusion principles holds, that is, no more than one herbivore species can persist on one limiting resource if this resource is provided by a single plant. \par

%\subsection*{Case 2: several plant species and one resource}
However, consider now %$p$ herbivore species competing for one resource ($R$) embedded into $n$ plants. 
that this resource ($R$) is provided by $n$ plants.
Herbivores have access to the resource through the consumption of several species of plants, depending on their feeding strategy.   
At steady state, it is possible to calculate $\barre{R}_{hi}$ for each herbivore $i$ (see appendix 2 for details):
\begin{equation}\label{oneresourcetwoplants}
\barre{R}_{hi}=\sum ^n _{j=1} \frac{S_j}{a_j+g_{ij}\barre{H}_i}Q_{v1R}
\end{equation}
For simplicity, consider the case where two herbivore species ($H_1$ and $H_2$) compete for one resource ($R$) embedded into two plants species ($V_1$ and $V_2$). Extending equation \ref{oneresourcetwoplants}, resource availabilities for each herbivore species at steady state are:
\begin{equation}
\barre{R}_{h1}=\frac{S_1}{a_1+g_{11}\barre{H}_1}Q_{v1R}+\frac{S_2}{a_2+g_{12}\barre{H}_1}Q_{v2R}
\end{equation}
and
\begin{equation}
\barre{R}_{h2}=\frac{S_1}{a_1+g_{21}\barre{H}_2}Q_{v1R}+\frac{S_2}{a_2+g_{22}\barre{H}_2}Q_{v2R}
\end{equation}
Clearly, the competition outcome depends on the foraging strategies of the competitors, more specifically, on the efficiencies of the consumption functions ($g_{ij}$). If $g_{11}>g_{21}$ and $g_{12}>g_{22}$, herbivore 1 consumes both plants more efficiently than its competitor. Thus, the competitive exclusion principle holds, and herbivore 2 is excluded. The reverse situation ($g_{11}<g_{21}$ and $g_{12}<g_{22}$) leads to the exclusion of herbivore 1. However, if the two herbivores are specialized on different plant species $g_{11}>g_{21}$ and $g_{12}<g_{22}$, or if $g_{11}<g_{21}$ and $g_{12}>g_{22}$, coexistence is possible. %Hence, in a case of a spatial segregation of the resource, the foraging strategy will be a crucial factor determining competition outcome. 
In other words, despite the fact that herbivores compete for a single resource, %as in case 1, 
the competitive exclusion principle does not necessarily hold. Indeed, %each plant species represents a spatial segregation of the resource, 
plants species create a spatial segregation of the resource, and the specialization of herbivores on different plant species, similar to niche segregation in space, makes coexistence possible.

\subsection*{Bottom-up stoichiometry}%{Case 3: competition model with one plant species and several resources}

Resource ratio in a given plant interacts with resource ratio of the herbivore, thus constraining persistence of herbivores. It is a bottom-up effect mediated by stoichiometry.
Consider $p$ herbivores feeding on one plant species embedding $k$ resources. According to the Liebig's law of the minimum expressed by the minimum function in equation 1, for each herbivore $i$ the interplay between resource requirement and resource availability will determine which resource is the most limiting for growth \citep{Grover1997}. Depending on their requirements, and on the ratios of resources available in plant biomass, two herbivores feeding on a single plant species may not be limited by the same resource. Thus, requirement differences among herbivores can be interpreted as niche segregation. %Yet, as we shall see, this niche segregation does not allow coexistence when two herbivore species feed on a single plant species.\\ 
For a single herbivore $i$, feeding on the plant, the level of limiting resource $R_u$ (with $u \in [1,k]$) in plant biomass at equilibrium writes (see appendix 3 for details):
\begin{equation}\label{resourceoneplant}
\barre{R}_{uhi}=\barre{V}|_{Ru}\; Q_{vRu} =\frac{m_i}{g_i}Q_{hiRu} 
\end{equation}
Where $\barre{V}|_{Ru}$ is plant biomass at steady state when $R_u$ is limiting. Similarly to former cases, this level represents the level of resource available to another herbivore and is therefore a key driver of competitive outcomes. It can be graphically represented by a zero net growth isocline (ZNGI) in the phase space of the $k$ resources in plant biomass. One can also represent how resources are consumed by the herbivore with a consumption vector in this phase space \citep{Tilman1980}. As for the classical resource-ratio theory \citep{Tilman1982}, we will show here that this graphical representation is a valuable tool to address the competitive outcomes between herbivore species. \par
For simplicity, consider two herbivore species ($H_1$ and $H_2$) competing for two resources ($R_1$ and $R_2$) embedded into a single plant species ($V$). According to equation \ref{resourceoneplant}, the slopes of the ZNGIs only depend on herbivore parameters, which are constant. Therefore, the ZNGIs are parallel to the axis on the phase plan $\{R_1,R_2\}$. According to the classic resource-ratio theory \citep{Tilman1982}, a first necessary condition for coexistence at equilibrium is that the ZNGIs of the two herbivores cross one another. A second necessary condition relies on the difference between the slopes of the consumption vectors of the competitors \citep{Tilman1982}.  The consumption vectors graphically illustrate how resource consumption drives the levels of resources from resource supply to equilibrium levels. In the phase plan, resource supply is represented by the supply point $S$, that is, the total amount of resources at equilibrium in absence of consumption:

\begin{equation}
S_{R_1}=Q_{vR_1}(S-a\barre{V})
\end{equation}
\begin{equation}
S_{R_2}=Q_{vR_2}(S-a\barre{V})
\end{equation}
For a given herbivore $i$, the consumption vector $\vec{C_i}$ writes:
\begin{equation}
\vec{C_i}=\left( 
\begin{array}{l}
g_i\barre{V}\barre{H}_i Q_{vR_1}\\
g_i\barre{V}\barre{H}_i Q_{vR_2}
\end{array}\right) 
=g_i\barre{V}\barre{H}_i \left( 
\begin{array}{l}
Q_{vR_1}\\
Q_{vR_2}
\end{array}\right) 
\end{equation}
The vectorÕs slope is determined by the ratios of resources embedded in plant biomass. An important consequence is that all herbivores have the same slope of consumption vector when feeding on a single given plant. This constraint precludes coexistence, and the resource-ratio embedded in plant biomass determines which of the competitor will displace the other (figure \ref{herbifig}). Hence, despite niche segregation on the requirement axe, two herbivores cannot coexist on two resources. This result is in contrast with the classic resource-ratio theory, which stipulates that two consumer may coexist on two resources. The reason is that classically, consumers are assumed to control the slope of their consumption vector \citep{Tilman1982}. This assumption is valid for primary producers, which take up essential nutrients independently in their environment, in the form of dissolved chemical molecules, but not for herbivores, which take up essential nutrients already bounded in plant biomass. Therefore, niche segregation alone cannot promote coexistence. Only herbivore that can match plant stoichiometry the best can persist and outcompete other herbivores. This leads to a strong bottom-up stoichiometric constraint.

@@

However, it is possible to define boundary ZNGI. Considering that herbivore $i$ can consume both plants, its foraging strategy will lie between exclusive consumption of plant 1, on one side, and exclusive consumption of plant 2, on the other side. Thus, boundary ZNGI slope writes (see appendix 4 for details):
\begin{equation}\label{boundaryZNGI}
\barre{R}_u=\frac{Q_{hiRu}m_i}{g_{ij}}
\end{equation}
This isocline $\barre{R}_u$ represents the ZNGI in the case where herbivore $i$ consumes only plant $j$ and is limited by nutrient $u$. In case on two plants consumed, the real $\barre{R}_u$ will lie between two boundary ZNGI (one for each plant).

By looking at boundary ZNGI equation (\ref{boundaryZNGI}), it appears that ZNGI slopes depends only on herbivore constant parameters. Therefore, it is parallel to the axis. Moreover, two herbivores having similar quotas but different feeding strategies would have different ZNGI. Thus, if boundary ZNGI of two herbivores cross each other, coexistence might be possible. \par

Next, competition outcome will depend on the relative orientation of the consumption vector of herbivores \citep{Tilman1980}. However, vector slope calculation is uneasy in the case of packaged resources because vector slope depends on plant supply points. Hence, for a given herbivore, vectors do not have a constant slope valid for all supply conditions. This is why instead of consumption vectors, the model allows the calculation of boundary vectors that determine an area in the phase plan where each herbivore species could coexist with an other one. It is possible to determine a boundary relation between plant supply points ($S_1$ and $S_2$) that allows each herbivore to consume both resources when one resource is limiting, and leads to $\barre{V}_1$ and $\barre{V}_2$ at steady state. These boundary supply points are $S_{1hi}$ and $S_{2hi}$ for plant 1 and 2 respectively (see appendix 4). Hence, boundary vector slopes are:
\begin{equation}
\vec{C}_{h1}= 
\begin{pmatrix}
\barre{S}_{1h1} \;Q_{v1R1}+\barre{S}_{2h1}\; Q_{v2R1} \\
\barre{S}_{1h1}\; Q_{v1R2}+\barre{S}_{2h1}\; Q_{v2R2} \\
\end{pmatrix} 
\end{equation}
\begin{equation}
\vec{C}_{h2}= 
\begin{pmatrix}
\barre{S}_{1h2} \;Q_{v1R1}+\barre{S}_{2h2}\; Q_{v2R1} \\
\barre{S}_{1h2}\; Q_{v1R2}+\barre{S}_{2h2}\; Q_{v2R2} \\
\end{pmatrix} 
\end{equation}
These two boundary vectors play a similar role as consumption vectors in Tilman's model. However, as resources are packaged into plants, vector slopes depend on the way herbivore species feed on plants containing resources.  
Hence, assuming plant 1 is richer in resource 1 ($Q_{v1R1}>Q_{v2R1}$), and plant 2 is richer in resource 2 ($Q_{v1R2}<Q_{v2R2}$), and assuming herbivore 1 is more limited by resource 1 ($Q_{h1R1}>Q_{h1R2}$), and herbivore 2 is more limited by resource 2 ($Q_{h2R1}<Q_{h2R2}$), three different strategies can be considered. The first one occurs when each herbivore species consumes preferentially the plant species which gives the greater quantity of the most limiting resource for this herbivore species, and which is less limiting for its competitor (i.e., $g_{11}>g_{12}$ and $g_{21}<g_{22}$). In that case, if we consider the boundary vectors for herbivore 1 and for herbivore 2, we can define several zones on the phase plan (see figure \ref{Coexistence}). The zone between the two boundary vectors represents the supply conditions allowing stable coexistence of the two herbivore species. Thus, each herbivore consumes the most profitable plant (i.e., quotas and consumption functions follow a similar trend), but each herbivore is specialized (more or less) on a different plant than its competitor, which promotes coexistence. \par
The second case represents the reverse situation, where each herbivore species consumes preferentially the plant species which provides greater quantity of the most limiting resource for its competitor (i.e., $g_{11}<g_{12}$ and $g_{21}>g_{22}$). Hence, the zone between the boundary vectors does not allow coexistence (see figure \ref{Exclusion}), and in many cases equation \ref{Systeme} does not have any realistic solution (with both herbivore species persisting). Thus, competitive exclusion is the general outcome. \par 
One can notice that plant stoichiometry constrains the supply point because of resource packaging into plants. 
%Last, due to resource packaging into plants, the supply point is constrained. 
Resource ratio within each plant will define a slope:
\begin{equation}
\alpha _{vj} = \frac{Q_{vjR2}}{Q_{vjR1}}
\end{equation}
In case of two plants, supply point will lie between the two extreme slopes ($\alpha _{v1}$ and $\alpha _{v2}$) defining a feasibility cone. Therefore, the whole phase plan is not available. Resource supply occurs only within this feasibility cone, which adds another constraint on herbivore persistence and competition.

Spatial segregation of resources embedded in plants and bottom-up stoichiometry are the two key points. If resources are not spatially decoupled or if herbivores do not have a feeding strategy that can compensate for the bottom-up stoichiometry imbalance, coexistence is impossible between herbivore species. The following cases illustrate this argument. 
A first case occurs when herbivore species are not selective at all: they consume plant species according to their respective biomass. In that case, both herbivores consume resources in the same way (i.e., $g_{11}=g_{21}$ and $g_{12}=g_{22}$). Hence, there is no segregation in herbivore consumption: all herbivore species have the same consumption vector, which is similar to the case where only one plant species is present (see figure \ref{herbifig}). Therefore, the trajectory will either cross herbivore 1 ZNGI first, and this herbivore will be excluded, or the trajectory will cross herbivore 2 ZNGI first, and this herbivore will be excluded. %Only a particular case, where the trajectory leads exactly on the crossing point, allows coexistence. \par
Coexistence will be unlikely because even if resources are spatially segregated, herbivores are constrained by plant stoichiometry. \par
%If we release the previous assumptions on herbivore and plant quotas (i.e., inequality for herbivore requirements, and inequality for plant profitability), two other situations can potentially occur.
A second case occurs when the previous assumptions on herbivore and plant quotas (i.e., inequality for herbivore requirements, and inequality for plant profitability) are released. %, which leads to two other situations.% can potentially occur.
Therefore, both herbivores can have the same quotas (i.e., $Q_{h1R1}=Q_{h2R1}$ and $Q_{h1R2}=Q_{h2R2}$) but different consumption functions. In that case, one plant will be more interesting for both herbivores (i.e., the plant that is richer for the most limiting resource). Hence, the herbivore that can consume this plant the most efficiently will exclude its competitor. Again, bottom-up stoichiometry constrained herbivore coexistence. 
Another case can occur when both plants have the same quotas (i.e., $Q_{v1R1}=Q_{v2R1}$ and $Q_{v1R2}=Q_{v2R2}$). In that case, the system is similar to the case where only one plant is present, which leads to competitive exclusion. Here, spatial segregation does not occur. \par

>>>>

Table \ref{Parametres} represents a review of the state variables and the parameters used in the model. %We analyze the model step-by-step, starting from a simple case with herbivores competing for one plant and one resource, then several plants and one resource, then multiple resources embedded into one plant, and finally the complete model, with multiple resources embedded into multiple plants.
Indeed, each plant provides several resources, and resources are provided by several plants. %, which create a new level of complexity.
The first case is a stoichiometric balance issue between plant and herbivore, while the second case is a spatial segregation of resources.

\subsection*{Bottom-up stoichiometry}%Case 1: one plant species and one resource}
%A given resources may be provided by only one plant or several plants, which creates a spatial segregation of resources. 
Herbivores might compete for one or several resources. 
First of all, consider a simple model with $p$ herbivore species feeding on one plant species embedding a single %chemical element 
resource. 
In case of one resource involved, this resource ($R$) is assumed to be growth limiting.

@@

\begin{equation}
 \barre{H}_i=\frac{g_iQ_{vR}S-aQ_{hiR}m}{g_iQ_{hiR}m}
 \end{equation}
Therefore, at equilibrium, herbivore biomass increases with plant availability (supply) and resource quota in plant biomass ($Q_{vR}$), while it decreases with herbivore mortality and resource quota in herbivore biomass ($Q_{hiR}$). Resource availability at steady state is: 
\begin{equation}\label{oneresource}
\barre{R}_{hi}=\barre{V}Q_{vR}=\frac{S}{a+g_i\barre{H}_i}Q_{vR}
\end{equation}
This $\barre{R}_{hi}$ represents level of resource remaining available for another herbivore, it also represents the minimal threshold of resource availability for herbivore species $i$ (i.e., if resource availability is below this threshold this herbivore species cannot maintain a population at steady state). Indeed, it can be assimilated to Tilman's $R^*$.
Therefore, considering two herbivores (species 1 and species 2), if $g_1\barre{H}_1>g_2\barre{H}_2$, species 1 depletes resource below the threshold of species 2, and species 2 is excluded. %Therefore, competition between two herbivore limited by the same chemical resource embedded into one plant leads to competitive exclusion. 
In other words, the competitive exclusion principles holds, that is, no more than one herbivore species can persist on one limiting resource if this resource is provided by a single plant. In other words, plant stoichiometry has an impact herbivore competition, which is a bottom-up stoichiometric constraint. \par
%Resource ratio in a given plant interacts with resource ratio of the herbivore, thus constraining persistence of herbivores. It is a bottom-up effect mediated by stoichiometry.
According to the classical resource-ratio theory \citep{Tilman1982}, increasing the number of resources considered should promote coexistence between consumers.  
Consider $p$ herbivores feeding on one plant species embedding $k$ resources. According to the Liebig's law of the minimum expressed by the minimum function in equation \ref{equaherbivoregeneral}, for each herbivore $i$ the interplay between resource requirement and resource availability will determine which resource is the most limiting for growth \citep{Grover1997}. Depending on their requirements, and on the ratios of resources available in plant biomass, two herbivores feeding on a single plant species may not be limited by the same resource. Thus, requirement differences among herbivores can be interpreted as niche segregation. %Yet, as we shall see, this niche segregation does not allow coexistence when two herbivore species feed on a single plant species.\\ 
\par
For a single herbivore $i$, feeding on the plant, the level of limiting resource $R_u$ (with $u \in [1,k]$) in plant biomass at equilibrium writes (see appendix 3 for details):
\begin{equation}\label{resourceoneplant}
\barre{R}_{uhi}=\barre{V}|_{Ru}\; Q_{vRu} =\frac{m_i}{g_i}Q_{hiRu} 
\end{equation}
where $\barre{V}|_{Ru}$ is plant biomass at steady state when $R_u$ is limiting. Similarly to former cases, this level represents the level of resource available to another herbivore and is therefore a key driver of competitive outcomes. It can be graphically represented by a zero net growth isocline (ZNGI) in the phase space of the $k$ resources in plant biomass. One can also represent how resources are consumed by the herbivore with a consumption vector in this phase space \citep{Tilman1980}. As for the classical resource-ratio theory \citep{Tilman1982}, we will show here that this graphical representation is a valuable tool to address the competitive outcomes between herbivore species. \par
For simplicity, consider two herbivore species ($H_1$ and $H_2$) competing for two resources ($R_1$ and $R_2$) embedded into a single plant species ($V$). According to equation \ref{resourceoneplant}, the slopes of the ZNGIs only depend on herbivore parameters, which are constant. Therefore, the ZNGIs are parallel to the axis on the phase plan $\{R_1,R_2\}$. According to the classical resource-ratio theory \citep{Tilman1982}, a first necessary condition for coexistence at equilibrium is that the ZNGIs of the two herbivores cross one another. A second necessary condition relies on the difference between the slopes of the consumption vectors of the competitors \citep{Tilman1982}.  The consumption vectors graphically illustrate how resource consumption drives the levels of resources from resource supply to equilibrium levels. In the phase plan, resource supply is represented by the supply point $S$, that is, the total amount of resources at equilibrium in absence of consumption:

\begin{equation}
S_{R_1}=Q_{vR_1}(S-a\barre{V})
\end{equation}
\begin{equation}
S_{R_2}=Q_{vR_2}(S-a\barre{V})
\end{equation}
For a given herbivore $i$, the consumption vector $\vec{C_i}$ writes:
\begin{equation}
\vec{C_i}=\left( 
\begin{array}{l}
g_i\barre{V}\barre{H}_i Q_{vR_1}\\
g_i\barre{V}\barre{H}_i Q_{vR_2}
\end{array}\right) 
=g_i\barre{V}\barre{H}_i \left( 
\begin{array}{l}
Q_{vR_1}\\
Q_{vR_2}
\end{array}\right) 
\end{equation}
The vectorÕs slope is determined by the ratios of resources embedded in plant biomass. An important consequence is that all herbivores have the same slope of consumption vector when feeding on a single plant. This constraint precludes coexistence, and the resource-ratio embedded in plant biomass determines which of the competitor will displace the other (figure \ref{herbifig}). Hence, despite niche segregation on the requirement axe, two herbivores cannot coexist on two resources. This result is in contrast with the classical resource-ratio theory, which stipulates that two consumer may coexist on two resources. The reason is that classically, consumers are assumed to control the slope of their consumption vector \citep{Tilman1982}. This assumption is valid for primary producers, which take up essential nutrients independently in their environment, in the form of dissolved chemical molecules, but not for herbivores, which take up essential nutrients already bounded in plant biomass. Therefore, niche segregation alone cannot promote coexistence. Only herbivore that can match plant stoichiometry the best can persist and outcompete other herbivores. This leads to a strong bottom-up stoichiometric constraint.

%\subsection*{Case 2: several plant species and one resource}
\subsection*{Spatial segregation of resources}
However, consider now %$p$ herbivore species competing for one resource ($R$) embedded into $n$ plants. 
that a limiting resource ($R$) is provided by $n$ plants.
Herbivores have access to the resource through the consumption of several species of plants, depending on their feeding strategy.   
At steady state, it is possible to calculate $\barre{R}_{hi}$ for each herbivore $i$ (see appendix 2 for details):
\begin{equation}\label{oneresourcetwoplants}
\barre{R}_{hi}=\sum ^n _{j=1} \frac{S_j}{a_j+g_{ij}\barre{H}_i}Q_{v1R}
\end{equation}
For simplicity, consider the case where two herbivore species ($H_1$ and $H_2$) compete for one resource ($R$) embedded into two plants species ($V_1$ and $V_2$). Extending equation \ref{oneresourcetwoplants}, resource availabilities for each herbivore species at steady state are:
\begin{equation}
\barre{R}_{h1}=\frac{S_1}{a_1+g_{11}\barre{H}_1}Q_{v1R}+\frac{S_2}{a_2+g_{12}\barre{H}_1}Q_{v2R}
\end{equation}
and
\begin{equation}
\barre{R}_{h2}=\frac{S_1}{a_1+g_{21}\barre{H}_2}Q_{v1R}+\frac{S_2}{a_2+g_{22}\barre{H}_2}Q_{v2R}
\end{equation}
Clearly, the competition outcome depends on the foraging strategies of the competitors, more specifically, on the efficiencies of the consumption functions ($g_{ij}$). If $g_{11}>g_{21}$ and $g_{12}>g_{22}$, herbivore 1 consumes both plants more efficiently than its competitor. Thus, the competitive exclusion principle holds, and herbivore 2 is excluded. The reverse situation ($g_{11}<g_{21}$ and $g_{12}<g_{22}$) leads to the exclusion of herbivore 1. However, if the two herbivores are specialized on different plant species $g_{11}>g_{21}$ and $g_{12}<g_{22}$, or if $g_{11}<g_{21}$ and $g_{12}>g_{22}$, coexistence is possible. %Hence, in a case of a spatial segregation of the resource, the foraging strategy will be a crucial factor determining competition outcome. 
In other words, despite the fact that herbivores compete for a single resource, %as in case 1, 
the competitive exclusion principle does not necessarily hold. Indeed, %each plant species represents a spatial segregation of the resource, 
plants species create a spatial segregation of the resource, and the specialization of herbivores on different plant species, similar to niche segregation in space, makes coexistence possible because herbivores can overcome the bottom-up stoichiometric constraint.

%{Case 3: competition model with one plant species and several resources}

@@

However, it is possible to define boundary ZNGI. Considering that herbivore $i$ can consume both plants, its foraging strategy will lie between exclusive consumption of plant 1, on one side, and exclusive consumption of plant 2, on the other side. Thus, boundary ZNGI slope writes (see appendix 4 for details):
\begin{equation}\label{boundaryZNGI}
\barre{R}_u=\frac{Q_{hiRu}m_i}{g_{ij}}
\end{equation}
This isocline $\barre{R}_u$ represents the ZNGI in the case where herbivore $i$ consumes only plant $j$ and is limited by nutrient $u$. In case of two plants consumed, the real $\barre{R}_u$ will lie between two boundary ZNGI (one for each plant).

By looking at boundary ZNGI equation (\ref{boundaryZNGI}), it appears that ZNGI slopes depend only on herbivore constant parameters. Therefore, it is parallel to the axis. Moreover, two herbivores having similar quotas but different feeding strategies would have different ZNGI. Thus, if boundary ZNGI of two herbivores cross each other, coexistence might be possible. \par

Next, competition outcome will depend on the relative orientation of the consumption vector of herbivores \citep{Tilman1980}. However, vector slope calculation is uneasy in the case of packaged resources because vector slope depends on plant supply points. Hence, for a given herbivore, vectors do not have a constant slope valid for all supply conditions. This is why instead of consumption vectors, the model allows the calculation of boundary vectors that determine an area in the phase plan where each herbivore species could coexist with an other one. It is possible to determine a boundary relation between plant supply points ($S_1$ and $S_2$) that allows each herbivore to consume both resources when one resource is limiting, and leads to $\barre{V}_1$ and $\barre{V}_2$ at steady state. These boundary supply points are $S_{1hi}$ and $S_{2hi}$ for plant 1 and 2 respectively (see appendix 4). Hence, boundary vector slopes are:
\begin{equation}
\vec{C}_{h1}= 
\begin{pmatrix}
\barre{S}_{1h1} \;Q_{v1R1}+\barre{S}_{2h1}\; Q_{v2R1} \\
\barre{S}_{1h1}\; Q_{v1R2}+\barre{S}_{2h1}\; Q_{v2R2} \\
\end{pmatrix} 
\end{equation}
\begin{equation}
\vec{C}_{h2}= 
\begin{pmatrix}
\barre{S}_{1h2} \;Q_{v1R1}+\barre{S}_{2h2}\; Q_{v2R1} \\
\barre{S}_{1h2}\; Q_{v1R2}+\barre{S}_{2h2}\; Q_{v2R2} \\
\end{pmatrix} 
\end{equation}
These two boundary vectors play a similar role as consumption vectors in Tilman's model. However, as resources are packaged into plants, vector slopes depend on the way herbivore species feed on plants containing resources.  
Hence, assuming plant 1 is richer in resource 1 ($Q_{v1R1}>Q_{v2R1}$), and plant 2 is richer in resource 2 ($Q_{v1R2}<Q_{v2R2}$), and assuming herbivore 1 is more limited by resource 1 ($Q_{h1R1}>Q_{h1R2}$), and herbivore 2 is more limited by resource 2 ($Q_{h2R1}<Q_{h2R2}$), two general strategies can be considered. The first one occurs when each herbivore species consumes preferentially the plant species which gives the greater quantity of the most limiting resource for this herbivore species, and which is less limiting for its competitor (i.e., $g_{11}>g_{12}$ and $g_{21}<g_{22}$). In that case, if we consider the boundary vectors for herbivore 1 and for herbivore 2, we can define several zones on the phase plan (see figure \ref{Coexistence}). The zone between the two boundary vectors represents the supply conditions allowing stable coexistence of the two herbivore species. Thus, each herbivore consumes the most profitable plant (i.e., quotas and consumption functions follow a similar trend), but each herbivore is specialized (more or less) on a different plant than its competitor, which promotes coexistence. \par
The second case represents the reverse situation, where each herbivore species consumes preferentially the plant species which provides greater quantity of the most limiting resource for its competitor (i.e., $g_{11}<g_{12}$ and $g_{21}>g_{22}$). Hence, the zone between the boundary vectors does not allow coexistence (see figure \ref{Exclusion}), and in many cases equation \ref{Systeme} does not have any realistic solution (with both herbivore species persisting). Thus, competitive exclusion is the general outcome. \par

Spatial segregation of resources embedded in plants and herbivore response to bottom-up stoichiometry are the two key points. If resources are not spatially decoupled or if herbivores do not have a feeding strategy that can compensate for the bottom-up stoichiometry imbalance, coexistence is impossible between herbivore species. The following cases illustrate this argument. 
A first case occurs when herbivore species are not selective at all: they consume plant species according to their respective biomass. In that case, both herbivores consume resources in the same way (i.e., $g_{11}=g_{21}$ and $g_{12}=g_{22}$). Hence, there is no segregation in herbivore consumption: all herbivore species have the same consumption vector, which is similar to the case where only one plant species is present (see figure \ref{herbifig}). Therefore, the trajectory will either cross herbivore 1 ZNGI first, and this herbivore will be excluded, or the trajectory will cross herbivore 2 ZNGI first, and this herbivore will be excluded. %Only a particular case, where the trajectory leads exactly on the crossing point, allows coexistence. \par
Coexistence will be unlikely because even if resources are spatially segregated, herbivores are constrained by plant stoichiometry. \par
%If we release the previous assumptions on herbivore and plant quotas (i.e., inequality for herbivore requirements, and inequality for plant profitability), two other situations can potentially occur.
A second case occurs when the previous assumptions on herbivore and plant quotas (i.e., inequality for herbivore requirements, and inequality for plant profitability) are released. %, which leads to two other situations.% can potentially occur.
Therefore, both herbivores can have the same quotas (i.e., $Q_{h1R1}=Q_{h2R1}$ and $Q_{h1R2}=Q_{h2R2}$) but different consumption functions. In that case, one plant will be more interesting for both herbivores (i.e., the plant that is richer for the most limiting resource). Hence, the herbivore that can consume this plant the most efficiently will exclude its competitor. Again, bottom-up stoichiometry constrained herbivore coexistence. 
Another case can occur when both plants have the same quotas (i.e., $Q_{v1R1}=Q_{v2R1}$ and $Q_{v1R2}=Q_{v2R2}$). In that case, the system is similar to the case where only one plant is present, which leads to competitive exclusion. Here, spatial segregation does not occur. \par
Last, one can notice that plant stoichiometry constrains the supply point because of resource packaging into plants. 
%Last, due to resource packaging into plants, the supply point is constrained. 
Resource ratio within each plant will define a slope:
\begin{equation}
\alpha _{vj} = \frac{Q_{vjR2}}{Q_{vjR1}}
\end{equation}
In case of two plants, supply point will lie between the two extreme slopes ($\alpha _{v1}$ and $\alpha _{v2}$) defining a feasibility cone. Therefore, the whole phase plan is not available. Resource supply occurs only within this feasibility cone, which adds another constraint on herbivore persistence and competition.
